Dataset-level report

### 2019-11-08 analysis/reports/dat_report_template.Rmd
fix misc abund report issue

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", this_dataset, ".sqlite")))
cache <- storr::storr_dbi("datatable", "keystable", db)

>>>>

if(this_dataset == "misc_abund_short") {
  cache_loc = "miscabund"
} else{
  cache_loc = this_dataset
}

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
cache <- storr::storr_dbi("datatable", "keystable", db)
